{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-11 thesis/landslide.tex
the busy bee moves randomly around the screen to show that the system is processing

The WBE, used to estimate total number of interleavings,
computes the {\em proportion} of the total size
that the already-explored branches are expected to comprise,
using DPOR's workqueue to anticipate how many unexplored marked branches remain.
This serves as a ``progress bar'' that represents the estimated overall progress,
approaching 1 (not necessarily monotonically) as exploration continues.

>>>>

The WBE, used to estimate total number of interleavings,
computes the {\em proportion} of the total size
that the already-explored branches are expected to comprise,
using DPOR's workqueue to anticipate how many unexplored marked branches remain.
This serves as a ``progress bar'' that represents the estimated overall progress \cite{progress-bar},
approaching 1 (not necessarily monotonically) as exploration continues.
